### 2023-01-15 tensor_clustering/ieee_revision/response_s2.tex

%         One possible remedy is to apply singular value decomposition to the \emph{square unfolding}~\citep{mu2014square}, $\Mat_{sq}(\cdot)$, of Bernoulli tensor $\tY \in \{0,1\}^{p_1 \times \cdots \times p_K}$. Specifically, we have $\mat_{sq} (\tY) \in \{0,1\}^{p^{\floor{K/2}} \times p^{\ceil{K/2}} }$ with entries $[\Mat_{sq}(\tY)](j_1, j_2) = \tY(i_1, \ldots, i_K)$, where
% \begin{align}
%     j_1 &= i_1 + p_1(i_2 - 1) + \cdots + p_1 \cdots p_{\floor{K/2}-1} (i_{\floor{K/2}} - 1),\\
%     j_2 &= i_{\ceil{K/2}} + p_{ \ceil{K/2}}(i_{\ceil{K/2}} - 1) + \cdots + p_{ \ceil{K/2}} \cdot p_{K-1} (i_K-1).
% \end{align}
% The square matricization $\Mat_{sq}(\tY)$ is an asymmetric matrix. We can interpret $\Mat_{sq}(\tY)$ as the adjacency matrix for a bipartite network with connections between two groups of node. The first and second groups have $p_1 \cdots p_{\floor{K/2}}$ and $ p_{\floor{K/2}} \cdots p_K$ nodes, respectively. The entry $[\Mat_{sq}(\tY)](j_1, j_2)$ with $j_1, j_2$ in above equations refer to the presence of connections between the nodes corresponding to combinations $(i_1, \ldots, i_{\floor{K/2}})$ and $(i_{\ceil{K/2}}, \ldots, i_K)$. We summarize the procedure in Sub-algorithm 3.

% \begin{algorithm}[h!]
% \caption*{\bf Sub-algorithm 3: Weighted higher-order initialization for Bernoulli observation}
% \vspace{.15cm}
% \begin{algorithmic}[1] 
% \INPUT Bernoulli tensor $\tY \in \{0,1\}^{p\times \cdots \times p}$, cluster number $r$, relaxation factor $\eta > 1$ in $k$-means clustering.
% \State  Let the matrix $\mat_{sq} (\tY) \in \{0,1\}^{p^{\floor{K/2}} \times p^{\ceil{K/2}} }$ denote the nearly square unfolded tensor. Compute the estimate $\tX'$, where
% \begin{equation}\label{eq:matrixsvd}
%     \hat \tX' = \argmin_{\text{rank}(\mat_{sq}(\tX)) \leq r^{\ceil{K/2}}} \onormSize{}{ \mat_{sq}(\tX) -  \mat_{sq}(\tY)}_F^2.
% \end{equation}
% \State Implement lines 3-5 of Sub-algorithm~\hyperref[alg:main]{1} with $\hat \tX$ replaced by $\hat \tX'$ in~\eqref{eq:matrixsvd}.
% \OUTPUT Initial clustering $z^{(0)} \leftarrow \hat z$.
% \end{algorithmic}
% \end{algorithm}

% \begin{prop}[Error for Bernoulli initialization]\label{cor:ber} Consider the Bernoulli dTBM in the parameter space $\tP$ and Assumption~\ref{assmp:min_gap} holds. Assume that $\mtheta$ is balanced and $\min_{i\in[p]}\theta(i) \geq c$ for some constant $c>0$. Let $ z^{(0)}$ denote the output of Sub-algorithm~3. With probability going to 1, we have
% \begin{equation}\label{eq:ini_b}
%  \ell(z^{(0)}, z) \lesssim \frac{r^K p^{- \floor{K/2} }}{\text{SNR}}, \quad \text{and} \quad L(z^{(0)}, z) \lesssim  {\sigma^2 r^K p^{-\floor{K/2}}}.
% \end{equation}
% \end{prop}

%  \begin{proof}[Proof of Proposition~\ref{cor:ber}] Note that $\Mat_{sq}(\tX) \in \bbR^{p^{\floor{K/2}} \times p^{\ceil{K/2}}}$ and $\text{rank}(\Mat_{sq}(\tX)) \leq r^{\ceil{K/2}}$. Apply Lemma~\ref{lem:lowrank_binary} with $\mY = \Mat_{sq}(\tY), \mX = \Mat_{sq}(\tX)$, and $\hat \mX = \Mat_{sq}(\hat \tX')$. With probability tending to 1 as $ p \rightarrow \infty$, we have 
%         \begin{equation}
%             \onormSize{}{\hat \tX' - \tX}_F^2 = \onormSize{}{\Mat_{sq}(\hat \tX') - \Mat_{sq}(\tX)}_F^2 \lesssim p^{\ceil{K/2}}.
%         \end{equation}
%         We then obtain the upper bound by using $\hat \tX'$ in place of $\hat \tX$ in Theorem~\ref{thm:initial}.\fixme{Miaoyan}{you did not mention anywhere in the proof where the assumptions of $\theta$ is used...Change ``we then obtain the upper bound....'' by the full proof.
%         }
%         \end{proof}

% \begin{lem}[Low-rank binary matrix estimation] \label{lem:lowrank_binary} Let $\mY \in \{0, 1\}^{m \times n}$ denote a binary matrix with independent Bernoulli entries. \fixme{Miaoyan}{remove binary. The proof does not use binary at all. Every mathematical Lemma should mention only *minimal* necessary conditions.  Never, never put redundant and useless conditions.} Suppose that $n \geq m$ and $\bbE[\mY] = \mX \in [0,1]^{m \times n}$ with fixed rank $\text{rank}(\mX) \leq r$. Consider the least square estimator 
%         \begin{equation}
%             \hat \mX = \argmin_{\mX' \in \bbR^{m \times n}, \text{rank}(\mX') \leq r} \onormSize{}{\mX' - \mY}_F^2.
%         \end{equation}
%         There exist positive constant $C_1, C_2$ such that
%         \begin{equation}
%             \onormSize{}{\hat \mX - \mX}_F^2 \leq C_1 nr,
%         \end{equation}
%         with probability at least $1 - \exp(-C_2 nr)$.
%         \end{lem}
%  "
%         \end{quote}

%         For self-consistency, we also attach the proof for Lemma~\ref{lem:lowrank_binary} in Appendix C here:
%         \begin{quote}
%         ``
%             \begin{proof}[Proof of Lemma~\ref{lem:lowrank_binary}] Note that $\onormSize{}{\hat \mX - \mY}_F^2 \leq \onormSize{}{\mX - \mY}_F^2$ by the definition of least square estimator. Re-arranging the terms, we have 
%         \begin{align}
%             \onormSize{}{\hat \mX - \mX}_F^2 & \leq 2 \ang{ \hat \mX - \mX, \mY - \mX} \\ & \leq 2 \onormSize{}{\hat \mX - \mX}_F \sup_{\mT \in \bbR^{m \times n}, \text{rank}(\mT) \leq 2r, \onormSize{}{\mT}_F = 1} \ang{\mT, \mY - \mX} \\
%             & \leq C  \onormSize{}{\hat \mX - \mX}_F \sqrt{nr}
%         \end{align}
%         with probability at least $1 - \exp(-C_2 nr)$ for some positive constant $C_2$, where the second inequality follows from \citet[Lemma 1]{wang2019multiway}\fixme{Miaoyan}{provide a full proof for self-containness.}, and the last inequality follows from \citet[Lemma E5]{han2022optimal} \fixme{Miaoyan}{Not reader friendly! This is a simple results in matrix theory. Do not over-complicate things by involving a harder lemma.
%         Find a textbook for easy formulation for reference. }under the matrix case and the fact that the Orlicz norm of Bernoulli noise $\onormSize{}{\mY_{ij} - \mX_{ij}}_{\varphi_2} = \sup_{q \geq 1} \bbE[|\mY_{ij} - \mX_{ij}|^q]^{1/q}/q^{1/2} \leq 1$ since $|Y_{ij} - X_{ij}| \leq 1$ for all $i \in [m], j \in [n]$.
%         \end{proof} "
%         \end{quote}

        \item \textit{Also, Comparison in Remark 3 seems unfair. While the final exponential error rate developed in this paper is tight, it requires quite stronger SNR for a warm initialization. So, it does not make sense to compare the final rate without talking about under what SNR conditions these rates are achievable. Could the authors compare the SNR conditions under which both methods (the proposed one and Ke et al., 2019) achieve exact recovery?}

        \textbf{Response:} It seems that reviewer intends to comment the Remark 8, which compares the error rates between our algorithm and \cite{ke2019community}, rather than the Remark 3 for degree assumption, which is irrelevant to algorithm performance. We answer this question with focus on the Remark 8.

        The method in \cite{ke2019community} adopts a signal notion based on the singular gap of the core tensor, denoted as $\Delta_{\rm singular}$. However, we are not able to infer the exact recovery of the spectral method by our angle-base SNR condition. There exists a case in which our algorithm achieves exact recovery but the spectral method in \cite{ke2019community} fails. Hence, for fair comparison, we compare the best performance of our algorithm and \cite{ke2019community} under the strongest signal setting of each model. We have added a new remark in Section~\ref{subsec:ber} and elaborated the comparison with \cite{ke2019community} with SNR consideration:
        \begin{quote}
        ``...
            \begin{customrmk}{10}[Comparison with previous methods]   Previous work \citep{ke2019community} develops a spectral clustering method for Bernoulli dTBM. \cite{ke2019community} adopts a different signal notion based on the singular gap in the core tensor, denoted as $\Delta_{\rm singular}$. By \citet[Theorem 1]{ke2019community}, the spectral method achieves exact recovery with $\Delta_{\rm singular} \gtrsim p^{-1/2}$. However, we are not able to infer the exact recovery of spectral method by our angle-base SNR condition. Consider an order-2 dTBM with $p > 2, \sigma^2 = 1$, $\mtheta = \mathbf{1}$, equal size assignment $|z^{-1}(a)| = p/r$ for all $ a \in [r]$, and core matrix $\mS = \mI_2$. The singular gap under this setting is $\Delta_{\rm singular} = \min\{ \lambda_1 - \lambda_2, \lambda_2 \} = 0$, where $\lambda_1 \geq \lambda_2$ are singular values of $\mS$. In contrast, our angle gap $\Delta_{\min}^2 = 2$ satisfies the SNR condition in Theorem~\ref{thm:refinement}. Then, our algorithm achieves the exact recovery, but the spectral method in \cite{ke2019community} fails.

Hence, for fair comparison, we compare the best performance of our algorithm and \cite{ke2019community} under the strongest signal setting of each model. Since both methods contain an iteration procedure, we set the iteration number to infinity to avoid the computational error. Considering the largest angle-based SNR $\asymp 1$ in Theorem~\ref{thm:refinement}, our Bernoulli clustering achieves exponential error rate of order $\exp(-p^{(K-1)})$; considering the largest singular gap $\Delta_{\rm singular} \asymp 1$ in Theorem 1 of \cite{ke2019community}, the spectral clustering has a polynomial error rate of order $p^{-2}$. Our algorithm still shows a better theoretical accuracy than the competitive work for Bernoulli observations.   "
            \end{customrmk}

        \end{quote}

        % In Remark 8, we compare the best performances that our algorithm and method in \cite{ke2019community} can achieve. Both methods contain an iteration procedure, and \cite{ke2019community} adopts a singular gap signal notion different with our angle gap notion. To obtain the best performance, we set the number of iterations to infinity for both methods to avoid computational error and consider the error rates under the strongest angle or singular based SNR, respectively.

        % We consider the algorithm error rates of both methods with infinity number of iterations and with the strongest angle and singular SNR

        % Since both methods contain an iteration procedure, we set both iteration numbers to infinity to avoid the computational error; we

    \end{enumerate}

    \item \textit{My second concern was on the imposed identifiability conditions and I think the authors have fully addressed it.}

    \item \textit{My last comment surrounding the two lower bounds is the major one, but I don’t think the authors have addressed it appropriately. }

    \textbf{Response:} This comment concerns the proving hardness of the lower bound statements in dTBM and the flaws in the proof of Theorem~\ref{thm:stats}. We separate the comment by these two aspects and address each aspect one-by-one.

    \begin{enumerate}[wide]
        \item \textit{The authors argued that ``Our results show the similar conclusion but under different conditions.”. I agree that $\Delta_{\rm ang}$ and $\Delta_{\rm Euc}$ (using the notation is the response) are different quantities and $\Delta_{\rm ang}$ can be much smaller than $\Delta_{\rm Euc}$ in the proposed setting. However, that does NOT affect the hardness in proving the lower bound statement. For simplicity, I will just show that for statistical lower bound, which claims that}
    \begin{equation}
        \inf_{\hat z} \sup_{(z,S, \theta) \in P(\gamma)} \bbE[p\ell(\hat z, z )] \geq 1.
    \end{equation}
    \textit{Here $P(\gamma)$ refers to the parameter space where the core tensor S satisfies $\Delta_{\rm ang}^2 /\sigma^2 \leq p^{\gamma}$  and $z, \theta$ satisfy some regularity conditions (e.g., balance). To prove the lower bound, it suffices to fix particular $\theta$ and $S$ and take supreme over the community variable $z$. Then, a trivial selection is to set $\theta_i = 1$ (homogeneous degree) and some S such that $\Delta_{\rm ang}/\Delta_{\rm Euc} = 1 + o(1)$. Such $S$ can be constructed randomly: $S_{ijk} = 1 + \epsilon_{ijk}$ where $\epsilon_{ijk}$  are independent mean-zero Gaussian with variance tends to zero. After constructing such $\theta_i$ and $S$, the heterogeneity issue vanishes and $\Delta_{\rm Euc}$ and $\Delta_{\rm ang}$ becomes equivalent.}

    \textit{The lower bounds arguments for TBM and dTBM become really different if the author considers the following stronger statement:}
    \begin{equation}
        \inf_{S \in P(\gamma)} \inf_{\hat z} \sup_{(z, \theta)} \bbE[p \ell(\hat z, z)] \geq 1
    \end{equation}
    \textit{This statement is stronger than the previous one, as it suggests statistical impossibility whenever the SNR condition is not met, while the current one actually suggests statistical impossibility for at least a specific $S$ that does not meet SNR requirement.}

    \textbf{Response:} 
    %The former part of the comment concerns the proving hardness of lower bound statements in dTBM compared with TBM. 
    We thank reviewer for the suggestions. In short, we have provided a stronger statistical impossibility statement for dTBM, inspired by the reviewer. With the new statement, we argue that dTBM-specific techniques are required to obtain our statistical and computational impossibilities, though the proof idea shares the same spirit with reviewer's proof in comment. We have made several revisions in Section~\ref{sec:limits}, Section~\ref{sec:tbm}, Section~\ref{sec:mainproof}, and Appendix~\ref{sec:statprove1} to address the comment. We attach each revision with explanations below.

    First, we have provided a new impossibility result in Theorem~\ref{thm:stats}. The new Theorem~\ref{thm:stats} suggests the statistical impossibility of dTBM whenever the core tensor $\tS$ leads to a SNR with signal exponent $\gamma < -(K-1)$. This new impossibility statement is stronger than previous one which suggests the worst case impossibility for a particular $\tS$. We quote the revised theorem and discussion in Section~\ref{sec:limits} here:

    \begin{quote}
    ``
    \begin{customthm}{2}[Statistical critical value]  Consider general Gaussian dTBMs with parameter space $\tP(\gamma)$ with $K\geq 1$. Then, we have the following statistical phase transition. 
    \begin{itemize}[wide]
    \item 
    \textbf{Impossibility.} Assume $r\lesssim p^{1/3}$. Let $\tP_{\tS}(\gamma) \coloneqq \{ \tS: c_3\leq \onormSize{}{\text{Mat}(\tS)_{a:}}\leq c_4, a\in[r]\} \cap \{ \tS: \Delta_{\min}^2 = p^{\gamma}\}$ denote the space for valid $\tS$ satisfying SNR condition~\eqref{eq:gamma}, and $\tP_{z ,\mtheta} \coloneqq \{ \mtheta\in\mathbb{R}^p_{+},\ 
{c_1p\over r}\leq |z^{-1}(a)|\leq {c_2 p\over r}, \onorm{\mtheta_{z^{-1}(a)}}_1=|z^{-1}(a)|, a \in [r] \}$ denote the space for valid $(z, \mtheta)$,  where $c_1, c_2, c_3, c_4$ are the constants in parameter space \eqref{eq:family}. If the signal exponent satisfies $\gamma < -(K-1)$, then, for any true core tensor $\tS \in \tP_{\tS}(\gamma)$, no estimator $\hat z_{\text{stat}}$ achieves exact recovery in expectation; that is,
    \begin{equation}
  \gamma< -(K-1) \quad \Rightarrow  \quad \liminf_{p \rightarrow \infty}\inf_{\tS \in  \tP_{\tS}(\gamma)}  \inf_{\hat z_{\text{stat}}}\sup_{ (z, \mtheta) \in \tP_{z, \mtheta}} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right]\geq 1.
\end{equation}
\end{itemize}
    \end{customthm} ... "
    \end{quote}

    \begin{quote}
        `` ...
        The proofs for the two parts in Theorem~\ref{thm:stats} are in the Appendix II, Section~\ref{sec:statprove1} and Section~\ref{sec:statprove2}, respectively. The first part of Theorem~\ref{thm:stats} demonstrates impossibility of exact recovery whenever the core tensor $\tS$ satisfies SNR condition~\eqref{eq:gamma} with exponent $\gamma < -(K-1)$. The proof is information-theoretical, and therefore the results apply to all statistical estimators, including but not limited to MLE and trace maximization~\citep{ghoshdastidar2017uniform}. The minimax bound~\eqref{eq:minminmax} indicates the worst case impossibility for a particular core tensor $\tS$ with signal exponent $\gamma < -(K-1)$; i.e., under the assumptions of Theorem~\ref{thm:stats}, 
\begin{equation}
    \gamma < -(K-1) \quad \Rightarrow \quad \liminf_{p \rightarrow \infty}  \inf_{\hat z_{\text{stat}}}\sup_{ (z,\tS, \mtheta) \in \tP(\gamma)} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right]\geq 1.
\end{equation}
Such worst case impossibility is frequently studied in related works \citep{han2020exact, gao2018community} while our lower bound~\eqref{eq:minminmax} provides a stronger impossibility statement for arbitrary core tensor with weak signal.   ..."
    \end{quote}

### 2023-01-15 tensor_clustering/ieee_revision/response_s2.tex

    Second, we have added proof sketches for the impossibility results to better highlight the dTBM-specific techniques we used. In fact, our proof idea is common in minimax analysis and shares the same spirit with reviewer's proof idea in the comment: find the lower bound of minimax error by constructing a particular set of true parameters. However, angle-based signal notion brings extra difficulties in parameter constructions, and the previous TBM construction is no longer applicable to address the arbitrariness of core tensor. We quote the new proof sketches in new Section~\ref{subsec:impossible} here:

    \begin{quote}
    `` ...

    The proofs of impossibility in Theorems~\ref{thm:stats} and \ref{thm:comp} share the same proof idea with \citet[Theorems 6 and 7]{han2020exact} and \citet[Theorem 2]{gao2018community}. In both proofs of statistical and computational impossibilities, the key idea is to construct a particular set of parameters to lower bound the minimax rate. Specifically, for statistical impossibility in Theorem~\ref{thm:stats}, we construct a particular $(z^*_{\rm stats}, \mtheta^*_{\rm stats})  \in \tP_{z, \mtheta} $ such that for all $\tS^* \in \tP_{\tS}(\gamma)$
\begin{equation}
    \inf_{\hat z_{\rm stats}} \sup_{(z, \mtheta) \in \tP_{z, \mtheta}} \bbE[p \ell(\hat z_{\rm stat}, z)] \geq \inf_{\hat z_{\rm stats}} \bbE[p \ell(\hat z_{\rm stat}, z_{\rm stats}^*)| (z^*_{\rm stats}, \tS^*,\mtheta^*_{\rm stats})] \geq 1;
\end{equation}
for computational impossibility in Theorem~\ref{thm:comp}, we construct a particular $(z^*_{\rm comp}, \tS^*_{\rm comp}, \mtheta^*_{\rm comp})$ $\in \tP(\gamma)$ such that 
\begin{equation}
    \inf_{\hat z_{\rm comp}} \sup_{(z, \tS, \mtheta) \in \tP(\gamma)} \bbE[p \ell(\hat z_{\rm comp}, z)] \geq \inf_{\hat z_{\rm comp}} \bbE[p \ell(\hat z_{\rm comp}, z_{\rm comp}^*)| (z^*_{\rm comp}, \tS^*_{\rm comp},\mtheta^*_{\rm comp})] \geq 1.
\end{equation}

The constructions of $(z^*_{\rm stats}, \mtheta^*_{\rm stats})$ and $(z^*_{\rm comp}, \tS^*_{\rm comp}, \mtheta^*_{\rm comp})$ are the most critical steps. With good constructions, the lower bound ``$\geq 1$" can be verified by classical statistical conclusions (e.g.\ Neyman-Pearson Lemma) or prior work (e.g.\ HPC Conjecture).

A notable detail in the proof of statistical impossibility is the arbitrariness of $\tS^*$. The first infimum over $ \tP_{\tS}(\gamma)$ in the minimax rate~\eqref{eq:minminmax} requires that the lower bound~\eqref{eq:stats_impo_sketch} holds for any $\tS^* \in \tP_{\tS}(\gamma)$. The arbitrary choice of $\tS^*$ brings extra difficulties in the parameter construction, and consequently a non-trivial $\mtheta^*_{\rm stats} \neq \mathbf{1}$ is chosen to address the arbitrariness. Previous TBM construction in the proof of \citet[Theorem 6]{han2020exact} with $\mtheta^*_{\rm stats} = \mathbf{1}$ is no longer applicable in our case. Meanwhile, our construction $(z^*_{\rm comp}, \tS^*_{\rm comp}, \mtheta^*_{\rm comp})$ leads to a rank-2 mean tensor to relate the HPC Conjecture while TBM \citet[Theorem 7]{han2020exact} constructs a rank-1 mean tensor. Hence, we emphasize that dTBM-specific techniques are required to obtain our impossibility results, though the proof idea is common for minimax lower bound analysis. ... "
    \end{quote}

    Here are two details differ with reviewer's comment. First, reviewer's construction with $\mtheta^* = \mathbf{1}$ is non-applicable for our new statistical impossibility. The TBM construction with $\mtheta^*_{\rm stats} = \mathbf{1}$ is not able to handle the arbitrary choice of $\tS^*$, because the Euclidean gap condition $\Delta_{\rm Euc}^2 \leq p^{\gamma}$ is not guaranteed with arbitrary $\tS^*$ satisfying $\Delta_{\rm ang}^2 \leq p^{\gamma}$; see Example \ref{example:euc_alg} in our main text. In consequence, we design a special $\mtheta^*_{\rm stats} \neq \mathbf{1}$ in the proof.
    %Because the core tensor $\tS$ with angle gap $\Delta_{\rm ang}^2 \leq p^{\gamma}$ is not guaranteed to have Euclidean gap $\Delta_{\rm Euc}^2 \leq p^{\gamma}$; see Example \ref{example:euc_alg} in our main text. In consequence, we construct a special $\mtheta^*_{\rm stats} \neq \mathbf{1}$ to address the arbitrariness of $\tS^*$ with angle gap requirement. 
    Second, we consider one particular core tensor $\tS^*$ at a time, rather than the random tensor with entries $\tS_{ijk}^* = 1 + \epsilon_{ijk}, \epsilon_{ijk} \sim N(0, \delta^2)$ for some $\delta \rightarrow 0$ as $p \rightarrow \infty$. The expectation in minimax error is taken with respect to the noise in observation, rather than the randomness in the true parameters.

    We have also revised the discussion in Section~\ref{sec:tbm} based on the new theorem and proof sketches:

    \begin{quote}
    ``...

    Third, from the perspective of proofs, we develop new dTBM-specific techniques to handle the extra degree heterogeneity. In our Theorem~\ref{thm:stats}, we construct a special non-trivial degree heterogeneity to establish the lower bound for arbitrary core tensor with small angle gap, while, TBM~\citep{han2020exact} considers the constructions without degree parameter.
%we consider the profile MLE by maximizing out the nuisance degree parameter, while TBM~\citep{han2020exact} considers the usual MLE without degree parameter.
In our Theorem~\ref{thm:comp}, we construct a rank-2 tensor to relate HPC conjecture to $\Delta^2_{\text{ang}}$, while TBM~\citep{han2020exact} constructs a rank-1 tensor to relate HPC conjecture to $\Delta^2_{\text{Euc}}$. The asymptotic non-equivalence between $\Delta^2_{\text{ang}}$ and $\Delta^2_{\text{Euc}}$ renders our proof technically more involved. ..."
    \end{quote}

    Last, we have added the comparison with TBM in terms of the stronger statistical impossibility. Though the presentation in the Theorem 6 of \cite{han2020exact} suggests a weaker worst case impossibility for TBM, the proof of Theorem 6 indeed implies a stronger statistical impossibility for arbitrary core tensor with small signal. Both models show similar conclusions under different signal notions again, but we emphasize that different techniques are required to address the different signal notions. We quote the new discussion in Section~\ref{sec:tbm} here:

    \begin{quote}
        `` ...

         Last, we discuss the statistical impossibility statements. Our Theorem~\ref{thm:stats} implies the statistical impossibility whenever the core tensor $\tS$ leads to an angle-based SNR below the critical threshold. The Theorem 6 in \cite{han2020exact} implies the worst case statistical impossibility for a particular core tensor $\tS$ with Euclidean-based SNR below the statistical limit. Hence, our Theorem~\ref{thm:stats} shows a stronger statistical impossibility for dTBM than that presented in TBM \citet[Theorem 6]{han2020exact}. However, inspecting the proof of \cite{han2020exact}, the proof of Theorem 6 indeed implies a stronger TBM impossibility statement for arbitrary core tensor; i.e.,
 \begin{equation}
     \gamma < -(K-1) \quad \Rightarrow \quad \liminf_{p \rightarrow \infty} \inf_{ \tS \in \tP_{\tS, {\rm TBM}} \cap \{\Delta_{\rm Euc}^2 = p^{\gamma} \} }\inf_{\hat z_{\rm stats}}  \sup_{z \in \tP_{z, {\rm TBM}}}  \bbE[p \ell(\hat z_{\rm stats}, z)] \geq 1,
 \end{equation}
 where $\tP_{\tS, {\rm TBM}}$ and $\tP_{z, {\rm TBM}}$ refer to the space for core tensor $\tS$ and assignment $z$ under TBM, respectively. Again, in terms of the strong statistical impossibility, both models show similar conclusions but under different conditions. Since two impossibilities consider different core tensor regimes with non-equivalent $\Delta^2_{\text{ang}}$ and $\Delta^2_{\text{Euc}}$, we emphasize that different proof techniques are required to obtain these similar conclusions.  See our proof sketch in Section~\ref{subsec:impossible}, Appendices~\ref{sec:statprove1} and \ref{sec:compprove1} for detail technical differences. "
    \end{quote}

    For self-consistency, we also attach the proof of the new impossibility theorem in Appendix~\ref{sec:statprove1}:

    \begin{quote}
    ``...
        \begin{proof}[Proof of Theorem~\ref{thm:stats} (Impossibility)]Consider the general asymetric dTBM~\eqref{eq:general_dtbm} in the special case that $p_k = p$ and $r_k = r$ for all $ k\in [K]$. For simplicity, we show the minimax rate for the estimation on the first mode $\hat z_1$; the proof for other modes are essentially the same.

   To prove the minimax rate~\eqref{eq:minminmax}, it suffices to take an arbitrary $\tS^* \in  \tP_{\tS}(\gamma)$ wih $\gamma < -(K-1)$ and construct $(z^*_k, \mtheta^*_k)$ such that 
   \begin{equation}
       \inf_{\hat z_1} \bbE \left[ p\ell(\hat z_1, z_1^*) | (z^*_k, \mtheta^*_k, \tS^*)  \right]\geq 1.
   \end{equation}

   We first define a subset of indices $T_k \subset [p_k], k \in [K]$ in order to avoid the complication of label permutation. Based on \citet[Proof of Theorem 6]{han2020exact}, we consider the restricted family of $\hat z_k$'s for which the following three conditions are satisfied:
   \begin{align}
       &\text{(a)}\ \hat z_k(i)=z_k(i) \text{ for all }i\in T_k; \quad \text{(b)} \ |T^c_k|\asymp {p\over r}; \\
       &\text{(c)}\ \min_{\pi\in \Pi}\sum_{i\in[p]}\ind\{\hat z_k(i) \neq \pi\circ z_k (i)\} = \sum_{i\in[p]}\ind\{\hat z_k(i) \neq  z_k (i)\},
   \end{align}
for all $k \in [K]$.
   Now, we consider the construction:
   \begin{enumerate}
       \item[(i)] $\{z_k^*\}$ satisfies properties (a)-(c) with misclassification sets $T_k^c$ for all $k \in [K]$;
       \item [(ii)] $\{\mtheta_k^*\}$ such that $\mtheta_k^*(i) \leq \sigma r^{(K-1)/2} p^{-(K-1)/2}$ for all $i \in T_k^c, k \in [K]$ and $\max_{k \in [K], a \in [r]} $ $\onormSize{}{\mtheta_{k, z^{*, -1}_k(a)}}^2_2 \asymp p/r$.
   \end{enumerate}
   % There exists a $(z^*, \mtheta^*) \in \tP_{z, \mtheta}$ satisfying the property (i) and (ii) when $r < p$; otherwise, when $r = p$, we must have $\mtheta^*(i) = 1$ due to the $\ell_1$ norm constraint and we can not satisfy the property (ii).

   Combining the inequalities (39) and (40) in the proof of Theorem 2 in \cite{gao2018community}, we have 
   \begin{align}
        & \inf_{\hat z_1 } \bbE \left[ \ell(\hat z_1, z_1^*) | (z^*_k, \mtheta^*_k, \tS^*)  \right] \geq  \\
        & \quad  \frac{C}{r^3 |T_1^c|} \sum_{i \in T_1^c} \inf_{\hat z_1  (i)} \{ \bbP[\hat z_1(i) = 1| z_1^*(i) = 2, z_k^*, \mtheta_k^*, \tS^*] +   \bbP[\hat z_1(i) = 2| z_1^*(i) = 1, z_k^*, \mtheta_k^*, \tS^*] \},
   \end{align}
   where $C$ is some positive constant,  $\hat z_1$ on the left hand side denote the generic assignment functions in $\tP(\gamma)$, and the infimum on the right hand side is taken over the generic assignment function family of $\hat z_1(i)$ for all nodes $i \in T_1^c$. Here, the factor $r^3=r\cdot r^2$ in~\eqref{eq:inf_lower} comes from two sources: $r^2\asymp {r\choose 2}$ comes from the multiple testing burden for all pairwise comparisons among $r$ clusters; and another $r$ comes from the number of elements $|T^c_k|\asymp p/r$ to be clustered.

   Next, we need to find the lower bound of the rightmost side in~\eqref{eq:inf_lower}. 
   %For simplicity, we show the bound for the mode-1 case $k = 1$ only. We drop the subscripts $1$ in $z_1, T_1, \mS_1, \mtheta_1$ and omit the repeated procedures for the cases of $k = 2,\ldots, K$. 
We consider the hypothesis test based on model~\eqref{eq:general_dtbm}. First, we reparameterize the model under the construction (i)-(ii).
\begin{equation}
    \mx_a^* = \off{\mat_1 \of{ \tS^*\times_2 \mTheta_2^* \mM_2^*\times_3\cdots \times_K \mTheta^*_K \mM_K^* }}_{a:}, \quad \text{for all} \ a \in [r],
\end{equation}
where $\mx_a^*$'s are centroids in $\bbR^{p^{K-1}}$. Without loss of generality, we consider the lower bound for the summand in~\eqref{eq:inf_lower} for $i=1$. The analysis for other $i\in T^c_1$ are similar. For notational simplicity, we suppress the subscript $i$ and write $\my, \theta^*, z$ in place of $\my_1, \mtheta_1^*(1)$ and $z_1(1)$, respectively. The equivalent vector problem for assessing the summand in~\eqref{eq:inf_lower} is
\begin{equation}
\my=\theta^* \mx_{z}^*+\me,
\end{equation}
where $z\in \{1,2\}$ is an unknown parameter, $\theta^* \in \bbR_+$ is the given heterogeneity degree, $\mx_1^*,\mx_2^*\in\bbR^{p^{K-1}}$ are given centroids, and $\me\in\bbR^{p^{K-1}}$ consists of i.i.d.\ $N(0,\sigma^2)$ entries.  Then, we consider the hypothesis testing under the model~\eqref{eq:z}:
\begin{equation}
 H_0: z = 1 \text{ and } \my = \theta^* \mx_1^* + \me \quad \leftrightarrow \quad H_1: z = 2 \text{ and } \my = \theta^* \mx_2^* + \me,
\end{equation}

%   For an arbitrary $i \in T_1^c$, the right hand side in \eqref{eq:inf_lower} corresponds to the following hypothesis test:
%   \begin{equation}\label{eq:hypo}
%       H_0: \my = \mtheta_1^*(i) \mx_1^* + \me \quad \leftrightarrow \quad H_1: \my = \mtheta_1^*(i) \mx_2^* + \me,
%   \end{equation}
%   where $\my = [\mat_1(\tY)]_{i:}$, $\mx_a^* = [\mat_1( \tS^* \times_2 \mTheta^* \mM_2^* \times_3 \cdots \times_K \mTheta^* \mM_K^*)]_{a:}$, and $\me$ consists of i.i.d.\ $N(0,\sigma^2)$ entries. 
   The hypothesis testing~\eqref{eq:test} is a simple versus simple testing, since the assignment $z$ is the only unknown parameter in the test. 
   By Neyman-Pearson lemma, the likelihood ratio test is optimal with minimal Type I + II error. Under Gaussian model, the likelihood ratio test of \eqref{eq:test} is equivalent to the least square estimator $\hat z_{LS} = \argmin_{a = \{1,2\}} \onormSize{}{\my - \theta^* \mx_a^*}_F^2$.

   Let $\mS = \mat_1(\tS)$. Note that 
   \begin{align}
       \onormSize{}{ \theta^* \mx_1^*  - \theta^* \mx_2^*}_F &\leq  \theta^* \onormSize{}{ \mS^*_{1:} - \mS^*_{2:} }_F \prod_{k = 2}^K \lambda_{\max}(\mTheta_k^*\mM_k^*)  \\
       & \leq \theta^* \onormSize{}{ \mS^*_{1:} - \mS^*_{2:} }_F   \max_{k \in [K]/\{1\}, a \in [r]} \onormSize{}{\mtheta_{k, z^{*, -1}_k(a)}}_2^{K-1} \\
       & \leq  \sigma r^{(K-1)/2} p^{-(K-1)/2} 2 c_4 p^{(K-1)/2} r^{-(K-1)/2}\\
       & \leq 2 c_4 \sigma, 
   \end{align}
%   \begin{align}
%       \onormSize{}{ \mtheta_1^*(i) \mx_1^*  - \mtheta_1^*(i) \mx_2^*}_F &\leq  \mtheta_1^*(i) \onormSize{}{ \mS^*_{1:} - \mS^*_{2:} }_F \prod_{k = 2}^K \lambda_{\max}(\mTheta_k^*\mM_k^*)  \\
%       & \leq \mtheta_1^*(i) \onormSize{}{ \mS^*_{1:} - \mS^*_{2:} }_F   \max_{k \in [K]/\{1\}, a \in [r]} \onormSize{}{\mtheta_{k, z^{*, -1}_k(a)}}_2^{K-1} \\
%       & \leq  \sigma r^{(K-1)/2} p^{-(K-1)/2} 2 c_4 p^{(K-1)/2} r^{-(K-1)/2}\\
%       & \leq 2 c_4 \sigma, \label{eq:bound}
%   \end{align}
   where $\lambda_{\max}$ denote the maximal singular value, the second inequality follows from Lemma~\ref{lem:singular_thetam}, and the third inequality follows from property (ii) and the boundedness constraint in $\tP_{\tS}(\gamma)$ such that $\onormSize{}{ \mS^*_{1:} - \mS^*_{2:} }_F  \leq \onormSize{}{\mS_{1:}^*}_F + \onormSize{}{\mS_{2:}^*}_F \leq 2c_4$.
